---
title: "Mousetracking Analysis"
author: "Laura Bock Paulsen"
date: "9/11/2022"
output: html_document
---

For the analysis of your very own mouse-tracking data, we will be using a package called MouseTrap. In order to get acquainted with the package, we will play around with data from a single participant conduction the circle-square experiment. 

The documentation for the package can be found here: <https://www.rdocumentation.org/packages/mousetrap/versions/3.1.5/topics/mousetrap>.

Use this page to solve the following steps by finding and applying appropriate mousetrap functions. Also, writing ?function_name() in the console is great way of reading about the function in question.

Call me for help whenever you get stuck (or take a quick look in the solutions file) :D


### Install packages and load in the data
```{r}

```

### Turn the data into a mousetrap object
Take a moment to look at the structure that it created. What are the elements, what information does it provide?
```{r}

```

### Make a quick plot using the mt_plot() function
Try to understand what the lines mean and how to “read” the graph. What seems weird about it when you think about how the experiment task looked like?
```{r}

```

### Make a plot in which the lines are coloured by condition
The demo-experiment had different trial types for which we have different predictions. Make a plot that distinguishes these two conditions, e.g. by different colors. 
```{r}

```

### Mirror-symmetric mapping of movements
Find a function that does a mirror-symmetric mapping of all the movements from the right side to the left side so that all movements overlap. Plot again. What does this function also do?
```{r}

```

### Plot timestamps by xpos
The standard plotting function shows x and y coordinates. Modify it so you plot timestamps by xpos. What do you see? What is this line in the beginning?
```{r}

```

### Find a function that removes the initial phase without mouse-movement
Find a function to remove this “line” and plot the timestamps by xpos again. 
```{r}

```

**Thought experiment:** If you now plotted x and y coordinates again, what would have changed in the plot? Think first, then try it! 
```{r}

```

### Time-normalize the data
Apply the function “mt_time_normalize”
```{r}

```

Now look at your data variable (the mt object) where a new matrix appeared. What do you notice? What does the function do? After you have thought about it yourself, check the documentation!

### Plot the normalized trajectories
Find out how to plot the normalized trajectories instead of the raw data.
```{r}

```

### Play around with the mt_time_normalize() function
Take a moment to play around with different numbers of steps in “mt_time_normalize” and see how that changes the shape of the trajectories, esp. when using very small numbers. Discuss what the decision about normalizing implies for the data analysis and interpretation. In the end, set the steps back to the default of 101.
```{r}

```

### Aggregated plots
Now we want to visualize our “findings”. Find a function that will plot averages of all the “similar” movements and all the “dissimilar” movements.
Think: Which trajectories do we need to use, the original or the time normalized? Why? Try plotting both to see whether you were right.
```{r}

```

### Apply the function mt_measures()
Apply the function “mt_measures” and look at the outcome in your data variable. 
```{r}

```

### Aggregating measures
Now find a function that helps you aggregate some measures of your pleasing over the two trial_types.
```{r}

```

### Interpret the results
Take a moment to think what these “results” could mean if this was a proper experiment which was not run by your instructor. How would you interpret this? Does this match your hypothesis? Especially look at the MAD (maximum absolute deviation from the direct path), the AUC (area under the curve) and the reaction time. 


## Additional exercises

### Removing incorrect trials
Normally, you'd want to remove incorrect trials. As the mouse_trap object does not function with tidyverse, figure out how to remove potential incorrect trials from your mousetrap object. 
```{r}

```

### Discussion of mt_align
Would the function ‘mt_align’ be useful for this data? Why or why not?
```{r}

```


### ggplot
As the mt_plot function uses ggplot, you can easily add themes, titles and such to make your plots look nice. Have a go at it!
```{r}

```

